Prizm Silver Rookie Cards

### 2024-04-25 paper/paper.qmd
updated read me and fixed citations

The analysis of these three datasets will be carried out using the statistical programming language `R` [@citeR], using the `tidyverse`[@citetidy], `here`[@citehere], and `readxl`[@citexl] packages. The figures and tables in the paper are generated using the, respectively, `ggplot2`[@citegg] and `knitr`[@citeknitr] packages.

>>>>

The analysis of these three datasets will be carried out using the statistical programming language `R` [@citeR], using the `tidyverse`[@tidyverse], `here`[@citehere], and `readxl`[@citexl] packages. The figures and tables in the paper are generated using the, respectively, `ggplot2`[@citegg] and `knitr`[@citeknitr] packages.
